Figures and tables for paper

### 2021-12-04 analysis/04_figs-tables.Rmd

```{r branding-contrasts}
# Pull the posterior draws for the organizations and compute contrasts
contrasts <- tibble(
  amnesty = draws %>% filter(level == "Amnesty International") %>% select(Gamma) %>% pull(),
  greenpeace = draws %>% filter(level == "Greenpeace") %>% select(Gamma) %>% pull(),
  oxfam = draws %>% filter(level == "Oxfam") %>% select(Gamma) %>% pull(),
  red_cross = draws %>% filter(level == "Red Cross") %>% select(Gamma) %>% pull()
) %>% 
  mutate(
    oxfam_amnesty = oxfam - amnesty,
    oxfam_greenpeace = oxfam - greenpeace,
    red_cross_amnesty = red_cross - amnesty,
    red_cross_greenpeace = red_cross - greenpeace,
  )

@@

```{r crackdown-contrasts-a}
# Pull the posterior draws for government crackdown
# Reference Level = Friendly relationship with government

@@

These data don't support our hypothesis; the Red Cross brand has an insignificant impact on likelihood to donate compared to both Greenpeace and Amnesty. While the contrasts for Oxfam are closer to being statistically significant, the effect is working in the other direction--Greenpeace and Amnesty both induce increased likelihood to donate on behalf of donors.

@@

```{r issue-contrasts-a}
# Pull the posterior draws for issue area
# Reference Level = Emergency Response
draws <- draws_intercepts
contrasts <- tibble(
  environment = draws %>% filter(level == "Environment") %>% select(Gamma) %>% pull(),
  human_rights = draws %>% filter(level == "Human rights") %>% select(Gamma) %>% pull(),
  refugee_relief = draws %>% filter(level == "Refugee relief") %>% select(Gamma) %>% pull()
  )

@@

contrasts_int <- tibble(
  environment = draws %>% filter(i == 5) %>% select(Gamma) %>% pull(),
  human_rights = draws %>% filter(i == 6) %>% select(Gamma) %>% pull(),
  refugee_relief = draws %>% filter(i == 7) %>% select(Gamma) %>% pull(),
  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
  criticized_environment = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  criticized_humanrights = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  criticized_refugee = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  crackdown_environment = draws %>% filter(i == 17) %>% select(Gamma) %>% pull(),
  crackdown_humanrights = draws %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  crackdown_refugee = draws %>% filter(i == 19) %>% select(Gamma) %>% pull(),
) %>% 
  mutate(
  criticized_refugee_environment = (criticized + refugee_relief + criticized_refugee) - (criticized + environment + criticized_environment),

@@

  crackdown_refugee_environment = (crackdown + refugee_relief + crackdown_refugee - crackdown + environment + crackdown_environment),

  crackdown_refugee_humanrights = (crackdown + refugee_relief + crackdown_refugee - crackdown + human_rights + crackdown_humanrights)
)

# Plot the contrasts
contrasts_int %>%
  pivot_longer(criticized_refugee_environment:crackdown_refugee_humanrights, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

@@

The generated contrasts don't provides results which are statistically significant. 0 is found within all intervals.

@@

contrasts_int <- tibble(
  few_wealthy_private_donors = draws %>% filter(i == 10) %>% select(Gamma) %>% pull(),
  government_grants = draws %>% filter(i == 11) %>% select(Gamma) %>% pull(),
  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
  criticized_wealthydonors = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  criticized_grants = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  crackdown_wealthydonors = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  crackdown_grants = draws %>% filter(i == 17) %>% select(Gamma) %>% pull(),
) %>% mutate(
  criticized_wealthydonors = (criticized + few_wealthy_private_donors + criticized_wealthydonors) - criticized,

  criticized_grants = (criticized + government_grants + criticized_grants) - criticized,

  crackdown_wealthydonors = (crackdown + few_wealthy_private_donors + crackdown_wealthydonors) - crackdown,

  crackdown_grants = (crackdown + government_grants + crackdown_grants) - crackdown
)

@@

The marginal posteriors for these contrasts are strange, but still tell us that the interaction between funding sources and government relationship produce no significant effects.

@@

```{r funding-contrasts-c}
# Overwrite draws with the appropriate interaction data
draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_4c.rds"))

@@

contrasts_int <- tibble(
  environment = draws %>% filter(i == 5) %>% select(Gamma) %>% pull(),
  human_rights = draws %>% filter(i == 6) %>% select(Gamma) %>% pull(),
  refugee_relief = draws %>% filter(i == 7) %>% select(Gamma) %>% pull(),
  few_wealthy_private_donors = draws %>% filter(i == 10) %>% select(Gamma) %>% pull(),
  government_grants = draws %>% filter(i == 11) %>% select(Gamma) %>% pull(),
  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
  emergency_crackdown_wealthydonors = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  emergency_crackdown_grants = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  environment_crackdown_wealthydonors = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  environment_crackdown_grants = draws %>% filter(i == 17) %>% select(Gamma) %>% pull(),
  humanrights_crackdown_wealthydonors = draws %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  humanrights_crackdown_grants = draws %>% filter(i == 19) %>% select(Gamma) %>% pull(),
  refugee_crackdown_wealthydonors = draws %>% filter(i == 20) %>% select(Gamma) %>% pull(),
  refugee_crackdown_grants = draws %>% filter(i == 21) %>% select(Gamma) %>% pull(),
) %>% 
  mutate(
  emergency_humanrights_wealthydonors = (crackdown + emergency_crackdown_wealthydonors) - (crackdown + few_wealthy_private_donors + human_rights + humanrights_crackdown_wealthydonors),

  emergency_humanrights_grants = (crackdown + emergency_crackdown_grants) - (crackdown + government_grants + human_rights + humanrights_crackdown_grants),

  emergency_environment_wealthydonors = (crackdown + emergency_crackdown_wealthydonors) - (crackdown + few_wealthy_private_donors + environment + environment_crackdown_wealthydonors),

  emergency_environment_grants = (crackdown + emergency_crackdown_grants) - (crackdown + government_grants + environment + environment_crackdown_wealthydonors),

  refugee_humanrights_wealthydonors = (crackdown + refugee_relief + refugee_crackdown_wealthydonors) - (crackdown + few_wealthy_private_donors + human_rights + humanrights_crackdown_wealthydonors),

  refugee_humanrights_grants = (crackdown + refugee_relief + refugee_crackdown_grants) - (crackdown + government_grants +  human_rights + humanrights_crackdown_grants),

  refugee_environment_wealthydonors = (crackdown + refugee_relief + refugee_crackdown_wealthydonors) - (crackdown + few_wealthy_private_donors + environment + environment_crackdown_wealthydonors),

  refugee_environment_grants = (crackdown + refugee_relief + refugee_crackdown_grants) - (crackdown + government_grants + environment + environment_crackdown_grants),

@@

Once again, we see some interesting distributions, but no results significant enough to confirm our hypothesis.

@@

```{r practices-contrasts-a}
# Pull the posterior draws for organizational practices
draws <- draws_intercepts
contrasts <- tibble(
  financial_transparency = draws %>% filter(level == "Financial transparency") %>% select(Gamma) %>% pull(),
  accountability = draws %>% filter(level == "Accountability") %>% select(Gamma) %>% pull()
)

# Plot the contrasts
contrasts %>%
  pivot_longer(financial_transparency, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

@@

contrasts_int <- tibble(
  fin_transparency = draws %>% filter(i == 8)%>% select(Gamma) %>% pull(),
  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
  financial_transparency_criticized = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  financial_transparency_crackdown = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  ) %>% mutate(
    financial_transparency_criticized = fin_transparency + criticized + financial_transparency_criticized,
    financial_transparency_crackdown = fin_transparency + crackdown + financial_transparency_crackdown
  )

@@

@@

```{r practices-contrasts-c}
# Overwrite draws with the appropriate interaction data
draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5c.rds"))

@@

contrasts_int <- tibble(
  fin_transparency = draws %>% filter(i == 8)%>% select(Gamma) %>% pull(),
  few_wealthy_private_donors = draws %>% filter(i == 10) %>% select(Gamma) %>% pull(),
  government_grants = draws %>% filter(i == 11) %>% select(Gamma) %>% pull(),
  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
  fin_smalldonors_criticized = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  fin_wealthydonors_criticized = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  fin_grants_criticized = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  fin_smalldonors_crackdown = draws %>% filter(i == 17) %>% select(Gamma) %>% pull(),
  fin_wealthydonors_crackdown = draws %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  fin_grants_crackdown = draws %>% filter(i == 19) %>% select(Gamma) %>% pull(),
  ) %>%
  mutate(
  fin_smalldonors_wealthydonors_criticized = (fin_transparency + criticized + fin_smalldonors_criticized) - (fin_transparency + criticized + few_wealthy_private_donors + fin_wealthydonors_criticized),

  fin_smalldonors_grants_criticized = (fin_transparency + criticized + fin_smalldonors_criticized) -  (fin_transparency + criticized + government_grants + fin_grants_criticized),

  fin_smalldonors_wealthydonors_crackdown = (fin_transparency + crackdown + fin_smalldonors_crackdown) - (fin_transparency + crackdown + few_wealthy_private_donors + fin_wealthydonors_crackdown),

  fin_smalldonors_grants_crackdown = (fin_transparency + crackdown + fin_smalldonors_crackdown) - (fin_transparency + crackdown + government_grants + fin_grants_crackdown)
  )

# Plot the contrasts
contrasts_int %>%
  pivot_longer(fin_smalldonors_wealthydonors_criticized:fin_smalldonors_grants_crackdown, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

@@

These intervals are massive; 0 is well within them, leaving us with insufficient evidence to confirm the hypothesis.

@@

```{r practices-contrasts-d}
# Overwrite draws with the appropriate interaction data
draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5d.rds"))

@@

contrasts_int <- tibble(
  fin_transparency = draws %>% filter(i == 8)%>% select(Gamma) %>% pull(),
  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
  environment = draws %>% filter(i == 5) %>% select(Gamma) %>% pull(),
  human_rights = draws %>% filter(i == 6) %>% select(Gamma) %>% pull(),
  refugee_relief = draws %>% filter(i == 7) %>% select(Gamma) %>% pull(),
  fin_emergency_criticized = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  fin_emergency_crackdown = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  fin_environment_criticized = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  fin_environment_crackdown = draws %>% filter(i == 17) %>% select(Gamma) %>% pull(),
  fin_humanrights_criticized = draws %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  fin_humanrights_crackdown = draws %>% filter(i == 19) %>% select(Gamma) %>% pull(),
  fin_refugee_criticized = draws %>% filter(i == 20) %>% select(Gamma) %>% pull(),
  fin_refugee_crackdown = draws %>% filter(i == 21) %>% select(Gamma) %>% pull()
  ) %>%
  mutate(
  fin_emergency_environment_criticized = (fin_transparency + criticized + fin_emergency_criticized) - (fin_transparency + criticized + environment + fin_environment_criticized),

  fin_emergency_humanrights_criticized = (fin_transparency + criticized + fin_emergency_criticized) - fin_transparency + criticized + human_rights + fin_humanrights_criticized,

  fin_emergency_environment_crackdown = (fin_transparency + crackdown + fin_emergency_crackdown) - (fin_transparency + crackdown + environment + fin_environment_crackdown),

  fin_emergency_humanright_crackdown = (fin_transparency + crackdown + fin_emergency_crackdown) - (fin_transparency + crackdown + human_rights + fin_humanrights_crackdown),

  fin_refugee_environment_criticized = (fin_transparency + criticized + fin_refugee_criticized) - (fin_transparency + criticized + environment + fin_environment_criticized),

  fin_refugee_humanright_criticized = (fin_transparency + criticized + fin_refugee_criticized) - (fin_transparency + criticized + human_rights + fin_humanrights_criticized),

  fin_refugee_environment_crackdown = (fin_transparency + crackdown + fin_refugee_crackdown) - (fin_transparency + crackdown + environment + fin_environment_crackdown),

  fin_refugee_humanright_crackdown = (fin_transparency + crackdown + fin_refugee_crackdown) - (fin_transparency + crackdown + human_rights + fin_humanrights_crackdown)
)

>>>>

```{r branding-contrasts}
# Pull the posterior draws for the organizations and compute contrasts
draws_intercepts <- draws

contrasts <- tibble(
  amnesty = draws %>% filter(level == "Amnesty International") %>% select(Gamma) %>% pull(),
  greenpeace = draws %>% filter(level == "Greenpeace") %>% select(Gamma) %>% pull(),
  oxfam = draws %>% filter(level == "Oxfam") %>% select(Gamma) %>% pull(),
  red_cross = draws %>% filter(level == "Red Cross") %>% select(Gamma) %>% pull()
) %>% 
  mutate(
    oxfam_amnesty = oxfam - amnesty,
    oxfam_greenpeace = oxfam - greenpeace,
    red_cross_amnesty = red_cross - amnesty,
    red_cross_greenpeace = red_cross - greenpeace,
  )

@@

```{r crackdown-contrasts-a}
# Pull the posterior draws for government crackdown
# Reference Level = Friendly relationship with government
draws_intercepts <- draws

@@

Although donors show significantly more willingness to donate to Red Cross when they are criticized or under crackdown from the host government, donors are less likely to donate to Oxfam under the same conditions. The only contrast which isn't statistically significant is the difference between Oxfam and Amnesty when both are under crackdown. All other contrasts do not contain 0 within their credibility interval.

@@

```{r issue-contrasts-a}
# Pull the posterior draws for issue area
# Reference Level = Emergency Response
draws <- draws_intercepts

contrasts <- tibble(
  environment = draws %>% filter(level == "Environment") %>% select(Gamma) %>% pull(),
  human_rights = draws %>% filter(level == "Human rights") %>% select(Gamma) %>% pull(),
  refugee_relief = draws %>% filter(level == "Refugee relief") %>% select(Gamma) %>% pull()
  )

@@

contrasts_int <- tibble(
  environment = draws %>% filter(i == 5) %>% select(Gamma) %>% pull(),
  human_rights = draws %>% filter(i == 6) %>% select(Gamma) %>% pull(),
  refugee_relief = draws %>% filter(i == 7) %>% select(Gamma) %>% pull(),
  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
  criticized_environment = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  criticized_humanrights = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  criticized_refugee = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  crackdown_environment = draws %>% filter(i == 17) %>% select(Gamma) %>% pull(),
  crackdown_humanrights = draws %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  crackdown_refugee = draws %>% filter(i == 19) %>% select(Gamma) %>% pull(),
) %>% 
  mutate(
    criticized_emergency_environment = (criticized) - (criticized + environment + criticized_environment),

  criticized_emergency_humanrights = (criticized) - (criticized + human_rights + criticized_humanrights),

  crackdown_emergency_environment = (crackdown) - (crackdown + environment + crackdown_environment),

  crackdown_emergency_humanrights = (crackdown) - (crackdown + human_rights + crackdown_humanrights),

  criticized_refugee_environment = (criticized + refugee_relief + criticized_refugee) - (criticized + environment + criticized_environment),

@@

  crackdown_refugee_environment = (crackdown + refugee_relief + crackdown_refugee) - (crackdown + environment + crackdown_environment),

  crackdown_refugee_humanrights = (crackdown + refugee_relief + crackdown_refugee) - (crackdown + human_rights + crackdown_humanrights)
)

# Plot the contrasts
contrasts_int %>%
  pivot_longer(criticized_emergency_environment:crackdown_refugee_humanrights, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

@@

Per our hypothesis, we expected to see the contrasts of the posterior distributions to be positive. However, only the contrasts between emergency response and the more contentious issue areas (environment and human rights) were positive, while contrasts between refugee relief and the more contentious issue areas were negative. Looking at all the contrasts, crackdown_refugee_environment, criticized_refugee_environment, and crackdown_emergency_humanrights contained 0 within their credibility interval.

@@

contrasts_int <- tibble(
  few_wealthy_private_donors = draws %>% filter(i == 10) %>% select(Gamma) %>% pull(),
  government_grants = draws %>% filter(i == 11) %>% select(Gamma) %>% pull(),
  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
  criticized_wealthydonors = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  criticized_grants = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  crackdown_wealthydonors = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  crackdown_grants = draws %>% filter(i == 17) %>% select(Gamma) %>% pull(),
) %>% mutate(
  criticized_wealthydonors = (criticized) - (criticized + few_wealthy_private_donors + criticized_wealthydonors),

  criticized_grants = (criticized) - (criticized + government_grants + criticized_grants),

  crackdown_wealthydonors = (crackdown) - (crackdown + few_wealthy_private_donors + crackdown_wealthydonors),

  crackdown_grants = crackdown - (crackdown + government_grants + crackdown_grants)
)

@@

All of the contrasts are positive and none of them contain 0 within their credibility interval, which supports our hypothesis that donors are more willing to donate to organizations supported by many small private donors and are under criticism or crackdown.

@@

```{r funding-contrasts-c}
# Overwrite draws with the appropriate interaction data
draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_4c.rds"))
# Draws for lower order interactions
draws_4b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_4b.rds"))
draws_3b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_3b.rds"))

@@

contrasts_int <- tibble(
  environment = draws %>% filter(i == 5) %>% select(Gamma) %>% pull(),
  human_rights = draws %>% filter(i == 6) %>% select(Gamma) %>% pull(),
  refugee_relief = draws %>% filter(i == 7) %>% select(Gamma) %>% pull(),
  few_wealthy_private_donors = draws %>% filter(i == 10) %>% select(Gamma) %>% pull(),
  government_grants = draws %>% filter(i == 11) %>% select(Gamma) %>% pull(),
  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
  crackdown_environment = draws_3b %>% filter(i == 17) %>% select(Gamma) %>% pull(),
  crackdown_humanrights = draws_3b %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  crackdown_refugee = draws_3b %>% filter(i == 19) %>% select(Gamma) %>% pull(),
  crackdown_wealthydonors = draws_4b %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  crackdown_grants = draws_4b %>% filter(i == 17) %>% select(Gamma) %>% pull(),
  emergency_crackdown_wealthydonors = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  emergency_crackdown_grants = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  environment_crackdown_wealthydonors = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  environment_crackdown_grants = draws %>% filter(i == 17) %>% select(Gamma) %>% pull(),
  humanrights_crackdown_wealthydonors = draws %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  humanrights_crackdown_grants = draws %>% filter(i == 19) %>% select(Gamma) %>% pull(),
  refugee_crackdown_wealthydonors = draws %>% filter(i == 20) %>% select(Gamma) %>% pull(),
  refugee_crackdown_grants = draws %>% filter(i == 21) %>% select(Gamma) %>% pull(),
) %>% 
  mutate(
  emergency_humanrights_wealthydonors = (crackdown) - (crackdown + few_wealthy_private_donors + human_rights + crackdown_humanrights + crackdown_wealthydonors + humanrights_crackdown_wealthydonors),

  emergency_humanrights_grants = (crackdown) - (crackdown + government_grants + human_rights + crackdown_humanrights + crackdown_grants + humanrights_crackdown_grants),

  emergency_environment_wealthydonors = (crackdown) - (crackdown + few_wealthy_private_donors + environment + crackdown_environment + crackdown_wealthydonors + environment_crackdown_wealthydonors),

  emergency_environment_grants = (crackdown) - (crackdown + government_grants + environment + crackdown_environment + crackdown_grants + environment_crackdown_grants),

  refugee_humanrights_wealthydonors = (crackdown + refugee_relief + crackdown_refugee) - (crackdown + few_wealthy_private_donors + human_rights + crackdown_humanrights + crackdown_wealthydonors + humanrights_crackdown_wealthydonors),

  refugee_humanrights_grants = (crackdown + refugee_relief + crackdown_refugee) - (crackdown + government_grants + human_rights + crackdown_humanrights + crackdown_grants + humanrights_crackdown_grants),

  refugee_environment_wealthydonors = (crackdown + refugee_relief + crackdown_refugee) - (crackdown + few_wealthy_private_donors + environment + crackdown_environment + crackdown_wealthydonors + environment_crackdown_wealthydonors),

  refugee_environment_grants = (crackdown + refugee_relief + crackdown_refugee) - (crackdown + government_grants + environment + crackdown_environment + crackdown_grants + environment_crackdown_grants),
  )

@@

Contrast is most likely improperly coded, gammas are all over the place, so no conclusions can be made regarding the hypothesis

@@

```{r practices-contrasts-a}
# Pull the posterior draws for organizational practices
draws <- draws_intercepts
contrasts <- tibble(
  fin_transparency = draws %>% filter(level == "Financial transparency") %>% select(Gamma) %>% pull(),
  accountability = draws %>% filter(level == "Accountability") %>% select(Gamma) %>% pull()
)

# Plot the contrasts
contrasts %>%
  pivot_longer(fin_transparency, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

@@

contrasts_int <- tibble(
  fin_transparency = draws %>% filter(i == 8)%>% select(Gamma) %>% pull(),
  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
  fin_transparency_criticized = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  fin_transparency_crackdown = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  ) %>% mutate(
    fin_transparency_criticized = (fin_transparency + criticized + fin_transparency_criticized) - (criticized),
    fin_transparency_crackdown = (fin_transparency + crackdown + fin_transparency_crackdown) - (crackdown)
  )

@@

The contrasts for hypothesis 5b provide evidence that donors are more willing to donate to organizations which are criticized or under crackdown and are also financially transparent.

@@

```{r practices-contrasts-c}
# Overwrite draws with the appropriate interaction data
draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5c.rds"))
# Lower order interaction draws
draws_5b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5b.rds"))
draws_4b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_4b.rds"))

@@

contrasts_int <- tibble(
  fin_transparency = draws %>% filter(i == 8)%>% select(Gamma) %>% pull(),
  few_wealthy_private_donors = draws %>% filter(i == 10) %>% select(Gamma) %>% pull(),
  government_grants = draws %>% filter(i == 11) %>% select(Gamma) %>% pull(),
  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
  criticized_wealthydonors = draws_4b %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  criticized_grants = draws_4b %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  crackdown_wealthydonors = draws_4b %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  crackdown_grants = draws_4b %>% filter(i == 17) %>% select(Gamma) %>% pull(),
  fin_transparency_criticized = draws_5b %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  fin_transparency_crackdown = draws_5b %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  fin_smalldonors_criticized = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  fin_wealthydonors_criticized = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  fin_grants_criticized = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  fin_smalldonors_crackdown = draws %>% filter(i == 17) %>% select(Gamma) %>% pull(),
  fin_wealthydonors_crackdown = draws %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  fin_grants_crackdown = draws %>% filter(i == 19) %>% select(Gamma) %>% pull(),
  ) %>%
  mutate(
  fin_smalldonors_wealthydonors_criticized = (fin_transparency + criticized + fin_transparency_criticized + fin_smalldonors_criticized) - (fin_transparency + criticized + few_wealthy_private_donors + criticized_wealthydonors + fin_transparency_criticized + fin_wealthydonors_criticized),

  fin_smalldonors_grants_criticized = (fin_transparency + criticized + fin_transparency_criticized + fin_smalldonors_criticized) -  (fin_transparency + criticized + government_grants + criticized_grants + fin_transparency_criticized + fin_grants_criticized),

  fin_smalldonors_wealthydonors_crackdown = (fin_transparency + crackdown + fin_transparency_crackdown + fin_smalldonors_crackdown) - (fin_transparency + crackdown + few_wealthy_private_donors + crackdown_wealthydonors + fin_transparency_crackdown + fin_wealthydonors_crackdown),

  fin_smalldonors_grants_crackdown = (fin_transparency + crackdown + fin_transparency_crackdown + fin_smalldonors_crackdown) - (fin_transparency + crackdown + government_grants + crackdown_grants + fin_transparency_crackdown + fin_grants_crackdown),

# additional contrasts to compare financial transparency to no transparency    
  not_fin_smalldonors_wealthydonors_criticized = (fin_transparency + criticized + fin_transparency_criticized + fin_smalldonors_criticized) - (criticized + few_wealthy_private_donors + criticized_wealthydonors),

  not_fin_smalldonors_grants_criticized = (fin_transparency + criticized + fin_transparency_criticized + fin_smalldonors_criticized) -  (criticized + government_grants + criticized_grants),

  not_fin_smalldonors_wealthydonors_crackdown = (fin_transparency + crackdown + fin_transparency_crackdown + fin_smalldonors_crackdown) - (crackdown + few_wealthy_private_donors + crackdown_wealthydonors),

  not_fin_smalldonors_grants_crackdown = (fin_transparency + crackdown + fin_transparency_crackdown + fin_smalldonors_crackdown) - (crackdown + government_grants + fin_transparency_crackdown + fin_grants_crackdown)
  )

# Plot the contrasts
contrasts_int %>%
  pivot_longer(fin_smalldonors_wealthydonors_criticized:not_fin_smalldonors_grants_crackdown, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

@@

Only fin_smalldonors_grants_crackdown contains 0 within its credibility interval. Since all other contrasts are positive and do not contain 0 within their credibility intervals, there is evidence supporting that donors are more willing to donate to NGOs that are criticized by the government/under government crackdown, are financially transparent, and are funded primarily by numerous small private donors.

@@

```{r practices-contrasts-d}
# Overwrite draws with the appropriate interaction data
draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5d.rds"))
# Lower-order interactions
draws_5b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5b.rds"))
draws_3b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_3b.rds"))

@@

contrasts_int <- tibble(
  fin_transparency = draws %>% filter(i == 8)%>% select(Gamma) %>% pull(),
  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
  environment = draws %>% filter(i == 5) %>% select(Gamma) %>% pull(),
  human_rights = draws %>% filter(i == 6) %>% select(Gamma) %>% pull(),
  refugee_relief = draws %>% filter(i == 7) %>% select(Gamma) %>% pull(),
  criticized_environment = draws_3b %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  criticized_humanrights = draws_3b %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  criticized_refugee = draws_3b %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  crackdown_environment = draws_3b %>% filter(i == 17) %>% select(Gamma) %>% pull(),
  crackdown_humanrights = draws_3b %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  crackdown_refugee = draws_3b %>% filter(i == 19) %>% select(Gamma) %>% pull(),
  fin_transparency_criticized = draws_5b %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  fin_transparency_crackdown = draws_5b %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  fin_emergency_criticized = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  fin_emergency_crackdown = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  fin_environment_criticized = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  fin_environment_crackdown = draws %>% filter(i == 17) %>% select(Gamma) %>% pull(),
  fin_humanrights_criticized = draws %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  fin_humanrights_crackdown = draws %>% filter(i == 19) %>% select(Gamma) %>% pull(),
  fin_refugee_criticized = draws %>% filter(i == 20) %>% select(Gamma) %>% pull(),
  fin_refugee_crackdown = draws %>% filter(i == 21) %>% select(Gamma) %>% pull()
  ) %>%
  mutate(
  fin_emergency_environment_criticized = (fin_transparency + criticized + fin_transparency_criticized + fin_emergency_criticized) - (fin_transparency + criticized + environment + fin_transparency_criticized + criticized_environment + fin_environment_criticized),

  fin_emergency_humanrights_criticized = (fin_transparency + criticized + fin_transparency_criticized + fin_emergency_criticized) - (fin_transparency + criticized + human_rights + fin_transparency_criticized + criticized_humanrights + fin_humanrights_criticized),

  fin_emergency_environment_crackdown = (fin_transparency + crackdown + fin_transparency_crackdown + fin_emergency_crackdown) - (fin_transparency + crackdown + environment + fin_transparency_crackdown + crackdown_environment + fin_environment_crackdown),

  fin_emergency_humanright_crackdown = (fin_transparency + crackdown + fin_transparency_crackdown + fin_emergency_crackdown) - (fin_transparency + crackdown + human_rights + fin_transparency_crackdown + crackdown_humanrights + fin_humanrights_crackdown),

  fin_refugee_environment_criticized = (fin_transparency + criticized + fin_transparency_criticized + criticized_refugee + fin_refugee_criticized) - (fin_transparency + criticized + environment + fin_transparency_criticized + criticized_environment + fin_environment_criticized),

  fin_refugee_humanright_criticized = (fin_transparency + criticized + fin_transparency_criticized + criticized_refugee + fin_refugee_criticized) - (fin_transparency + criticized + human_rights + fin_transparency_criticized + criticized_humanrights + fin_humanrights_criticized),
